Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/introduction.tex
foo

We consider the following TSP-related problems.  The {\em 2-edge-connected subgraph problem (2EC)} want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.  We formally define TAP in Section~\ref{experiment}.

@@

Known polyhedral structure makes it easier to study integrality gaps for such problems. Carr and Ravi \cite{carr-ravi} introduced fundamental extreme points. A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.  We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle. An FEP of order $k$ could represent an instance with many more than $k$ vertices. Carr and co-authors~\cite{CV,carr-ravi, Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp. 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp. 2EC) is bounded above by $C$. Thus we can create the ``hardest'' LP solutions to decompose.

>>>>

We consider the following TSP-related problems.  The {\em 2-edge-connected subgraph problem (2EC)} is to find a minimum-weight 2-edge-connected (multigraph) subgraph
% (which can multiple copies of each edge)
in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.  We formally define TAP in Section~\ref{experiment}.

@@

Known polyhedral structure makes it easier to study integrality gaps for such problems. Carr and Ravi \cite{carr-ravi} introduced fundamental extreme points. A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.  We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle. An FEP of order $k$ could represent an instance with many more than $k$ vertices. Carr and co-authors~\cite{CV,carr-ravi, BC11} proved that showing that $Cx$ is a convex combination of tours (resp. 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp. 2EC) is bounded above by $C$. Thus we can create the ``hardest'' LP solutions to decompose.
